\documentclass[11pt]{article}
\usepackage{enumitem}
 
\begin{document}

    \title {Interview Questions}
    \author {
        Fida Kamal\\
        \texttt{180041208}
        \and
        Fariha Fairoz Nohan\\
        \texttt{180041214}
        \and
        Alvi Aveen Khan\\
        \texttt{180041229}
    }
    \maketitle
    
    \section {Introduction}
 
    \begin{enumerate}
        \item This session is being recorded. Is that alright with you?
        \item Could you please tell us a little bit about yourself before we begin?
    \end{enumerate}
    
    \section {History of Making Donations}
    
    \begin{enumerate}
        \item Have you ever made donations in the past?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If they do not give a detailed answer) Could you tell us a little about how exactly you made these donations? (Was it a charity organization? Was it through friends arranging a small event?)
            \item (If the answer did not specify what was donated) What sort of things did you donate there?
            \item (If they do not mention monetary donations) Did you make any monetary donations?
        \end{enumerate}
        
        \item What were the outcomes of these donations? Did you ever find out?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If yes) How did you find out?
            \item (If no) Would you have preferred to know?
        \end{enumerate}
        
        \item Do you think we should include a feature in our application to inform users about the outcomes of their donations?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If yes) How do you think we should do this?
        \end{enumerate}
        
        \item How about a page with the history of all the donations you’ve made? How does that sound?
    \end{enumerate}
    
    \section {Problems with Existing System}
    
    \begin{enumerate}
    
        \item (If they did not mention formal charities)
        
        \begin{enumerate}[label=(\alph*)]
            \item Can I ask why you never donated through any charities?
            \item Did it ever feel like you couldn’t find a charity that was doing some specific work that you feel is important?
        \end{enumerate}
        
        \item (If they do mention formal charities)
        
        \begin{enumerate}[label=(\alph*)]
            \item When you were donating through these charities, did you face any difficulties?
            \item Were you able to find organizations that you liked and that you were assured were doing work that you supported?
        \end{enumerate}
    
    \end{enumerate}
    
    \section {System being Developed}
    
    \begin{enumerate}
    
        \item What do you think about the system that we are proposing, one which would bring together the different charities under one application? Do you think it would help solve the problems that you faced?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If yes) How do you think this could help? Do you think it would make it more likely for you to donate more often?
            \item (If no) Could I ask why you feel that way?
        \end{enumerate}
        
        \item One of the things that occurred to us while we thought about the application was how users are able to tell if a charity is reliable or not. Could you please share your thoughts on this topic?
        
        \item Do you think we should include a feature to help users of our application tell if a particular charity is reliable?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If yes) How do you think we can do this?
        \end{enumerate}
        
        \item With regard to the day-to-day activities of the many different charities that exist, have you ever had difficulties keeping track of what they were doing and how you could help?
        
        \begin{enumerate}[label=(\alph*)]
            \item (If yes) What were the problems you faced? How do you propose we go about fixing these problems in our system?
            \item (If no) How do you stay up-to-date about their activities?
        \end{enumerate}
    
    \end{enumerate}
    
    \section {Conclusion}
    
    \begin{enumerate}
    
        \item Do you have any more suggestions for us? Any ideas about features we could add?
    
    \end{enumerate}
 
\end{document}